\huge Tor's Usability for Censorship Circumvention

### 2016-04-14 pets2017-paper/pets2017-paper.tex
Fix tab:environments.
I had transposed it.
add in demographic information.

\begin{table}
\centering
\begin{tabular}{r c c c}
& E1 & E2 & E3 \\
% \noalign{\hrule}
websites blocked & X & & \\
public relays blocked & X & X & \\
default bridges blocked & X & X & X \\
\end{tabular}
\caption{
Summary of our simulated censorship environments.
E1 only requires participants to click ``Connect'';
E2 requires selection of an included bridge;
and E3 requires selection of a specific included bridge,
or manual configuration of a custom bridge.
E2's blocking is a superset of E1's;
similarly E3's is a superset of E2's.
}
\label{tab:environments}
\end{table}

@@

Out of our 16 participants, ages ranged from {\color {red} TODO}
(sigma = {\color {red} TODO}). {\color {red} TODO} of our participants had at least
a college education. {\color {red} TODO} had heard of Tor previously, 
and {\color {red} TODO} had used Tor previously. {\color {red} TODO} out of 
16 did not use any circumvention tools.

@@

Out of our 124 participants, ages ranged from {\color {red} TODO}
(sigma = {\color {red} TODO}). {\color {red} TODO} were male and 
{\color {red} TODO} of our participants had at least a college education.

>>>>

\begin{table}
\centering
\begin{tabular}{r c c c}
& E1 & E2 & E3 \\
% \noalign{\hrule}
websites blocked & X & X & X \\
public relays blocked & & X & X \\
default bridges blocked & & & X \\
\end{tabular}
\caption{
Summary of our simulated censorship environments.
E1 only requires participants to click ``Connect'';
E2 requires selection of an included bridge;
and E3 requires selection of a specific included bridge,
or manual configuration of a custom bridge.
E2's blocking is a superset of E1's;
similarly E3's is a superset of E2's.
}
\label{tab:environments}
\end{table}

@@

Out of our 16 participants, ages ranged from 20 to 62
(mu= 24.5, sigma = 12.6). 53.3\% were male. 
93.3\% of our participants had at least
a college education. 5 had previously heard of Tor but not used it, while 
and 5 had used Tor previously.

@@

Out of our 124 participants, 59 were recruited from the Xlab pool and the other 65 were
recruited from Craiglist. Ages ranged from 18 to 68
(mu = 28.9, sigma = 12). 56.8\% were male and 
84.8\% of our participants had at least a college education.
